A* with Perfect Heuristic/Potentials in Road Networks

### 2020-07-27 paper/ch_potentials.tex
changed to AAAI 2020 style

\documentclass[sigconf]{acmart}
%This is a template for producing LIPIcs articles.
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling cleveref support, use "autoref"

\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage[algo2e,vlined]{algorithm2e}

@@

%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{A* with Perfect Heuristic/Potentials in Road Networks}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Strasser}
\email{academia@ben-strasser.net}
\orcid{1234-5678-9012}
\affiliation{}

\author{Tim Zeitz}
\email{tim.zeitz@kit.edu}
\affiliation{%
  \institution{Institute of Theoretical Informatics, Algorithmics I, Karlsruhe Institute of Technology}
  \city{Karlsruhe}
  \country{Germany}
}

@@

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}
\ccsdesc[500]{Theory of computation~Shortest paths}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{shortest path, road graphs, goal-directed search, contraction hierarchy, heuristic search}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
% \begin{teaserfigure}
%   \includegraphics[width=\textwidth]{sampleteaser}
%   \caption{Seattle Mariners at Spring Training, 2010.}
%   \Description{Enjoying the baseball game from the third-base
%   seats. Ichiro Suzuki preparing to bat.}
%   \label{fig:teaser}
% \end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

% \appendix

\end{document}

>>>>

\def\year{2021}\relax
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai20}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{graphicx}  % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS

\usepackage{amssymb}
\usepackage{amsmath}

\setcounter{secnumdepth}{1} %May be changed to 1 or 2 if section numbers are desired.

%This is a template for producing LIPIcs articles.
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling cleveref support, use "autoref"

\usepackage{booktabs}
\usepackage[algo2e,vlined]{algorithm2e}

\pdfinfo{
/Title (A* with Perfect Heuristic/Potentials in Road Networks)
/Author (Ben Strasser, Tim Zeitz)
/Keywords (shortest path, road graphs, goal-directed search, contraction hierarchy, heuristic search)
}
\title{A* with Perfect Heuristic/Potentials in Road Networks}
\author{Ben Strasser\\
academia@ben-strasser.net\\
\And
Tim Zeitz\\
tim.zeitz@kit.edu\\
Karlsruhe Institute of Technology
}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
%\author{
%Ben Strasser

%\author{Tim Zeitz}
%tim.zeitz@kit.edu}
%\affiliation{%
%  \institution{Institute of Theoretical Informatics, Algorithmics I, Karlsruhe Institute of Technology}
%  \city{Karlsruhe}
%  \country{Germany}
%}

@@

\maketitle

@@

@@

\bibliography{dblp}
\bibliography{references}
\bibliographystyle{aaai}
\end{document}
